### 2010-06-18 code/subarchitectures/visualization.sa/trunk/doc/v11n.tex
v11n: html plugins work if nspluginwrapper is uninstalled; disabled -- a nasty bug needs more work

The new subarchitecture must be added to the main file CMakeLists.txt of the 
project. It should be added before any subarchitectures that use visualization
so that the dependent libraries will build correctly. Add the following
block before the first subarchitecture in CMakeLists.txt:

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   option(BUILD_SA_V11N "Build visualization libraries (Requires QT4)" NO)
   if(BUILD_SA_V11N)
      set(VISUALIZATION_INCLUDE_DIRS
         ${COGX_ROOT}/subarchitectures/visualization.sa/src/c++/autogen
         ${COGX_ROOT}/subarchitectures/visualization.sa/src/c++/core
         )
      set(VISUALIZATION_LIBRARIES
         DisplayClient VisualizationData
         )
      add_subdirectory(subarchitectures/visualization.sa)
      add_definitions(-DFEAT_VISUALIZATION)
   endif(BUILD_SA_V11N)
\end{Verbatim}

>>>>

The new subarchitecture must be added to the main CMakeLists.txt file of the 
project. It should be added before any subarchitectures that use visualization
so that the dependent libraries will build correctly. Add the following
block before the first subarchitecture in CMakeLists.txt:

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   include(subarchitectures/visualization.sa/cmake/v11n.cmake)
\end{Verbatim}
